### 2016-07-13 NLO.tex
Becky's remarks

\section{Squark Production at One-Loop}
This section discusses the cross section for squark production at next-to-leading order $\sigma^{\mathrm{NLO}}$. To do so, the next section gives a justification why on-shell renormalization has been chosen in section \ref{sec:renMRSSM}. After that, the set up of the calculation, which has been performed by a \texttt{C++} program,  of the different contributions to $\sigma^{\mathrm{NLO}}$, is explained. This includes a remark on how the calculation was sped up. Finally the results of the computation are presented in the form of $K$-factors. These are then compared to the ones in the MSSM before the thesis closes with an discussion of the behavior of $\sigma^{\mathrm{NLO}}$ in the limit of large sgluon masses.

@@

Considering a physical process with kinematics $\vec{k}_1 \hdots \vec{k}_n \to \vec{p}_1 \hdots \vec{p}_m$ and taking for the sake of simplicity only one scalar field $\phi$ the Fourier transform of the time ordered product of a correlation function is related to the corresponding S-matrix element like\footnote{In this subsection the $\sim$ indicates that the poles on either side are the same provided that all momenta are close to their mass shell, i.e. $p_i^0 \to E_{\vec{p}_i}$ and $k_j^0 \to E_{\vec{k}_j}$.}

@@

\sim \prod_{i=1}^n \frac{i\sqrt{Z}}{p_i^2 - m^2 + i\epsilon} \prod_{j=1}^m \frac{i\sqrt{Z}}{k_j^2 - m^2 + i\epsilon} \left\langle \left.\left.\vec{p}_1 \hdots \vec{p}_n \right| S \right| \vec{k}_1 \hdots \vec{k}_m \right\rangle .\label{eq:LSZ}

@@

Here $\mathcal{T}$ denotes the time ordering operator, $\left.| \Omega \right\rangle$ is the ground state of the interacting theory and $\sqrt{Z}$ is the residue of the single particle pole in the two-point function 

@@

@@

\caption{Diagrammatic figure of the two-point function of a scalar field: The propagator in an interaction theory can be calculated in a perturbation series in the coupling constant.}\label{fig:fullpropagator}

@@

\left[ p^2 - m_0^2 - \Sigma(p^2)\right]_{p^2 = m^2} = 0

@@

p^2 - m_0^2 - \Sigma(p^2) = (p^2 - m^2)\left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)_{p^2 = m^2} + \mathcal{O}((p^2 - m^2)^2).

@@

Z = \left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)_{p^2 = m^2}^{-1}.

@@

Now considers the full $(n+m)$-point function in scalar theory. One can decompose it into an amputated $(n+m)$-point function and ``full'' propagators like written in eq. \eqref{eq:propagator} and depicted in fig. \ref{fig:fullpropagator}.

@@

	\draw[fill=black] (80:1.5) circle (.01);
	\draw[fill=black] (90:1.5) circle (.01);
	\draw[fill=black] (100:1.5) circle (.01);
	\draw[fill=black] (-80:1.5) circle (.01);
	\draw[fill=black] (-90:1.5) circle (.01);
	\draw[fill=black] (-100:1.5) circle (.01);
\end{tikzpicture}
\caption{Diagrammatic figure of a ``full'' $(n+m)$-point function. Apart from the ``full'' propagators there is the ``full'' amputated $(n+m)$-point function}
\end{center}
\end{figure}\\
Inserting the expression
\begin{align}
\frac{i}{p^2 - m_0^2 - \Sigma(p^2)} \sim \frac{i Z}{p^2 - m^2}
\end{align}
for the full propagators one notices the same singularity as in eq. \eqref{eq:LSZ}. Comparing the coefficients of these poles in eq. \eqref{eq:LSZ} one obtains
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=2.0 pt, scale=1.3, arrow/.style={thick,->,shorten >=2pt,shorten <=2pt,>=stealth}]
	\node at (-4,0) {$\left\langle \left.\left.\vec{p}_1 \hdots \vec{p}_n \right| S \right| \vec{k}_1 \hdots \vec{k}_m \right\rangle =\sqrt{Z}^{n+m} \cdot$};
	\draw (0,0) circle (.75);
	\node at (0,0) {Amp.};

@@

	\draw[fill=black] (80:1.1) circle (.01);
	\draw[fill=black] (90:1.1) circle (.01);
	\draw[fill=black] (100:1.1) circle (.01);
	\draw[fill=black] (-80:1.1) circle (.01);
	\draw[fill=black] (-90:1.1) circle (.01);
	\draw[fill=black] (-100:1.1) circle (.01);
\end{tikzpicture}
\end{center}
\end{figure}\\
Now it becomes clear, why the renormalization in the on-shell scheme
\begin{align}
\left.\frac{\partial \Sigma(p^2)}{\partial p^2}\right|_{p^2 = m^2} \stackrel{!}{=} 0
\end{align}
introduces no further modification, when turning from the Green function to the S-matrix-element because $Z = 1$ in on-shell renormalization. Furthermore the on-shell condition for the mass renormalization
\begin{align}
\Sigma(p^2)|_{p^2 = m^2} = 0
\end{align}
means that the physical mass equals the tree level mass.

\subsection{The Squark Production Cross Section at Next-to-Leading Order}
The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born (tree-level) cross section, the virtual and the real corrections. 
\begin{align}
\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}\label{eq:BVR}
\end{align}
All three contributions have to be calculated with next-to-leading order parton density functions and $\alpha_s$. There are seven mass scales: the squark mass $m_{\tilde{q}}$, the gluino mass $m_{\tilde{g}}$, the center of mass energy of the colliding protons which is set to $\sqrt{S} = \unit[13]{TeV}$, the top-quark mass which is fixed to $m_t = \unit[172]{GeV}$, the mass of the pseudoscalar $m_{\sigma}$ and the renormalization and factorization scale. They have been set to $\mu_F = \mu_R = m_{\tilde{q}}$. The next section summaries how the calculation has been automated within a \texttt{C++} program.

@@

	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{R}|^2}$};
	\node [block1a] at (-1,-8) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to \sum |\mathcal{M}^{\mathrm{B}|^2}$};	

@@

	\node [block5b] at (7.5,-7.35) (Virt) {\underline{Virtual correction}\newline \texttt{LoopTools} $\to$ \newline computation of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$ };
	\node [block5c] at (11.5,-5.1) (Real) {\underline{Real correction}\newline phase space slicing: \newline $\bullet$ soft/collinear part \newline from \texttt{Mathematica},\newline \texttt{CUBA} three dimen- \newline sional integration to $\sigma^{\mathrm{R}}_{\mathrm{S}}$ and $\sigma^{\mathrm{R}}_{\mathrm{HC}}$ \newline $\bullet$ hard non-collinear \newline part from \newline \texttt{MADGRAPH}, \newline  \texttt{CUBA} $\to$ seven \newline dimensional \newline integration to $\sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$ \newline $\sigma^{\mathrm{R}} = \sigma^{\mathrm{R}}_{\mathrm{S}} + \sigma^{\mathrm{R}}_{\mathrm{HC}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};

@@

\caption{This scheme illustrates the setup of the computation of the next-to-leading order cross section. The (absolute) squared matrix amplitudes of the Born contribution the virtual correction and the real correction in the soft and/or collinear limit are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code. The amplitude from the real corrections is analytically integrated over the gluon's four momentum in $D$ dimensions. Loop integrals are evaluated numerically using \texttt{Looptools}. For the hard non-collinear regime, the matrix amplitude of the real corrections is imported from \texttt{MadGraph5}. The \texttt{CUBA}-library was used for all three contributions to perform the remaining integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$.}\label{fig:CalcSetup}

@@

The computation of the real corrections have been done by Wojciech Kotlarski, another member of the group. To extract the singularities from the real corrections, the ``two cut phase space slicing method'' outlined in section \ref{sec:RealGluonRad}, has been used. For the soft and hard collinear limit, the absolute squared matrix element has been calculated with \texttt{FormCalc} and analytically integrated over the gluon's four-momentum in $D$ dimensions in \texttt{Mathematica}. This has been exported to the \texttt{C++} code to perform the rest of the integration numerically with the \texttt{CUBA} library. The matrix element in the hard non-collinear regime has been imported from \texttt{MadGraph5}\cite{Alwall:2014hca} and the whole integration has been performed numerically by the \texttt{CUBA} library.\\

@@

It has been checked that for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$, the double as well as the single poles of the virtual and real correction cancel up to machine precision. Regarding the virtual corrections, this has been done by numerically extracting the $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$ coefficient of loop integrals (see the discussion in section \ref{sec:SetLambdaExplanation} for more details).\\

@@

For the discussion of results it will not been distinguished between virtual and real corrections. This is because they have not been separated strictly in the calculation: As already discussed both $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$ are divergent, i.e. there are poles of the form $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$. But these pole cancel exactly. On the other hand there are also prefactors from the phase space integral and the loop integral, with can be expanded in a power series in $\epsilon$. In short, the virtual and real correction to the cross section can be expressed with some coefficients $A$ - $E$, which are functions of the parameters $m_{\tilde{g}}$, $m_{\tilde{q}}$ and $m_{\sigma}$, in the following way:

@@

Some of the prefactors, namely $P_1$ and $P_2$, are the same in both contributions. Keeping them in eq. \eqref{eq:prefactoredecomp}, would slow the computation of the real part down by a factor of about five because this part of the calculation is done analytically. Therefore a speed-up can been achieved by discarding the common prefactors at the cost of loosing track about the origin of the next-to-leading order correction.\\
One common prefactor comes from the two-body phase space integral in eq. \eqref{eq:diffsigma}

@@

In addition the prefactor of a loop integral defined in \texttt{LoopTools} differs from the one usually (and therefore also here) used. The \texttt{LoopTools} definition\cite{LoopToolsManual} of a loop integral is 

@@

where $T^1$ is an $A$-integral, $T^2$ is an $B$-integral, etc. and $r_\Gamma = \frac{\Gamma(1-\epsilon)^2\Gamma(1+\epsilon)}{\Gamma(1-2\epsilon)}$, where $\Gamma(z)$ is the Gamma function. Comparing the prefactors of eq. \eqref{eq:LoopToolsInt} and eq.  \eqref{eq:LoopInt} one finds that one has to multiply the \texttt{LoopTools} output by

@@

in order to have the same prefactors as in eq. \eqref{eq:LoopInt}. Without going into detail why these factors are chosen, the right hand side of eq. \eqref{eq:PhasePrefactor} and eq. \eqref{eq:LoopPrefactor} are the prefactors discarded in the computation. Instead the prefactor $\left( 1 + \frac{\pi^2}{6}\epsilon^2 \right)$ has been included in the virtual correction. Therefore $P_1$ and $P_2$ are chosen like

@@

P_1 &=  2\ln 4\pi - 2\gamma_E - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} \\
P_2 &=  -\ln 4\pi \cdot\ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} + \frac{1}{2} \ln^2 \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}  + \gamma_E^2 - \frac{\pi^2}{3} + \ln^2 4\pi - 2\gamma_E\ln 4\pi + \gamma_E \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}  \nonumber

@@

It can be seen that the  $K$-factor increases with increasing squark mass and decreases with increasing gluino mass. Note, that the sum of virtual and real corrections gets negative for very light squarks. But this region of parameter space is already excluded experimentally.

@@

Note further, that within the real corrections, only gluon radiation is included. This is because quark radiation, as described in section \ref{sec:RealQuarkRad}, involves the treatment of on-shell singularities which have unfortunately not been dealt with, due to a limited time budget. However, \cite{Gavin:2013kga} suggests that quark radiation gives only a sub percent effect to the next-to-leading order cross section of squark production when $m_{\tilde{g}} < m_{\tilde{q}}$. Of course, this argument applies to the MSSM but as the only difference to the MRSSM comes from diagrams involving gluinos and sgluons it provides also a strong argument for the suppression of quark radiation in the MRSSM. In fact, sgluons do not appear at all in diagrams contributing to real corrections. Furthermore, the change from Majorana to Dirac gluinos can never imply an amplification of processes involving gluinos. The reason for this is that if a gluino undergoes, due to its mass, a chirality flip, the right handed part of it, namely the octino, does neither couple to quarks nor to squarks. However, the effect of quark radiation is thought to increase when $m_{\tilde{g}} > m_{\tilde{q}}$. This is quantified within the next section, when squark production is discussed in the MSSM. Nonetheless, quark radiation is by no means to be thought of a dominant contribution to squark production at next-to-leading order.\\

@@

\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$  in the MRSSM for a selected set of masses. The pseudoscalar mass is fixed to \mbox{$m_{\mathrm{\sigma}} = \unit[5000]{GeV}$}. For $\sigma^{\mathrm{LO}}$ parton density functions \texttt{MMHT2014LO} (LHAPDF ID: $25000$) is used, whereas for $\sigma^{\mathrm{NLO}}$ \texttt{MMHT2014NLO} (LHAPDF ID: $25100$) is used.}\label{tab:MRSSMKfactors}

@@

It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{q}}}{m_{\tilde{g}}}$ but not that strongly on the masses itself. This is also depicted in fig. \ref{fig:Kfactor_MRSSM} which shows the $K$-factors in the $m_{\tilde{q}}$-$m_{\tilde{g}}$ plane. The contour lines follow approximately rays from the origin. By performing the calculation without the shuffling of prefactors as explained in section \ref{sec:prefactors}, the raising of the $K$-factors for increasing values of $\frac{m_{\tilde{q}}}{m_{\tilde{g}}}$ has been traced down to the real corrections. As quark radiation is not included, this effect can further be pinned down to originate from the diagrams in fig. \ref{fig:RealGluon}. However, at least for small $m_{\tilde{g}}$, fig. \ref{fig:Kfactor_MRSSM} suggests that the $K$-factors drop again for increasing $m_{\tilde{q}}$.

>>>>

\section{Squark Production at One-Loop}
This section discusses the cross section for squark production at next-to-leading order $\sigma^{\mathrm{NLO}}$. To do so, the next section gives a justification why on-shell renormalization has been chosen in section \ref{sec:renMRSSM}. After that, the setup of the calculation of the different contributions to $\sigma^{\mathrm{NLO}}$, which has been performed by a \texttt{C++} program, is explained. This includes a remark on how the calculation was sped up. Finally the results of the computation are presented in the form of $K$-factors. These are then compared to the ones in the MSSM before the thesis closes with a discussion of the behavior of $\sigma^{\mathrm{NLO}}$ in the limit of large sgluon masses.

@@

Considering a physical process with kinematics $\vec{k}_1 \hdots \vec{k}_n \to \vec{p}_1 \hdots \vec{p}_m$ and taking only one scalar field $\phi$ for the sake of simplicity, the Fourier transform of the time ordered product of a correlation function is related to the corresponding S-matrix element like\footnote{In this section, $\sim$ indicates that the poles on either side are the same provided that all four-momenta are close to their mass shell, i.e. $p_i^0 \to E_{\vec{p}_i}$ and $k_j^0 \to E_{\vec{k}_j}$.}

@@

\sim \prod_{i=1}^n \frac{i\sqrt{Z}}{p_i^2 - m^2 + i\epsilon} \prod_{j=1}^m \frac{i\sqrt{Z}}{k_j^2 - m^2 + i\epsilon} \left\langle \vec{p}_1 \hdots \vec{p}_n \left| S \left| \vec{k}_1 \hdots \vec{k}_m \right\rangle\right.\right. .\label{eq:LSZ}

@@

Here $\mathcal{T}$ denotes the time ordering operator, $\left.| \Omega \right\rangle$ is the ground state of the interacting theory and $\sqrt{Z}$ is the residue of the single particle pole\footnote{Note that this does not coincide with the renormalization constant $Z$ in eq. \eqref{eq:renconst}.} in the ``full'' two-point function 

@@

which is diagrammatically shown in fig. \ref{fig:fullpropagator}.

@@

\caption{Diagrammatic figure of the ``full'' two-point function of a scalar field: The propagator in an interaction theory can be calculated in a perturbation series in the coupling constant.}\label{fig:fullpropagator}

@@

\left[ p^2 - m_0^2 - \Sigma(p^2)\right]_{p^2 = m^2} = 0.

@@

p^2 - m_0^2 - \Sigma(p^2) = \left.(p^2 - m^2)\left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)\right|_{p^2 = m^2} + \mathcal{O}((p^2 - m^2)^2).

@@

Z = \left.\left( 1 - \frac{\partial \Sigma(p^2)}{\partial p^2} \right)^{-1}\right|_{p^2 = m^2}.

@@

Now consider the full $(n+m)$-point function, depicted in fig. \ref{fig:fullvertex}, in scalar theory. One can decompose it into an amputated $(n+m)$-point function and ``full'' propagators like written in eq. \eqref{eq:propagator} and depicted in fig. \ref{fig:fullpropagator}.

@@

	\draw[fill=black] (80:1.5) circle (.01);
	\draw[fill=black] (90:1.5) circle (.01);
	\draw[fill=black] (100:1.5) circle (.01);
	\draw[fill=black] (-80:1.5) circle (.01);
	\draw[fill=black] (-90:1.5) circle (.01);
	\draw[fill=black] (-100:1.5) circle (.01);
\end{tikzpicture}
\caption{Diagrammatic figure of a ``full'' $(n+m)$-point function. Apart from the ``full'' propagators there is the ``full'' amputated $(n+m)$-point function.}\label{fig:fullvertex}
\end{center}
\end{figure}\\
Inserting the expression
\begin{align}
\frac{i}{p^2 - m_0^2 - \Sigma(p^2)} \sim \frac{i Z}{p^2 - m^2}
\end{align}
for the full propagators, one notices the same singularity as in eq. \eqref{eq:LSZ}. Comparing the coefficients of these poles in eq. \eqref{eq:LSZ}, one obtains
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=2.0 pt, scale=1.3, arrow/.style={thick,->,shorten >=2pt,shorten <=2pt,>=stealth}]
	\node at (-4,0) {$\left\langle \vec{p}_1 \hdots \vec{p}_n \left| S \left| \vec{k}_1 \hdots \vec{k}_m \right\rangle \right.\right. =\sqrt{Z}^{n+m} \cdot$};
	\draw (0,0) circle (.75);
	\node at (0,0) {Amp.};

@@

	\draw[fill=black] (80:1.1) circle (.01);
	\draw[fill=black] (90:1.1) circle (.01);
	\draw[fill=black] (100:1.1) circle (.01);
	\draw[fill=black] (-80:1.1) circle (.01);
	\draw[fill=black] (-90:1.1) circle (.01);
	\draw[fill=black] (-100:1.1) circle (.01);
\end{tikzpicture}.
\end{center}
\end{figure}\\
Now it becomes clear, why the renormalization in the on-shell scheme
\begin{align}
\left.\frac{\partial \Sigma(p^2)}{\partial p^2}\right|_{p^2 = m^2} \stackrel{!}{=} 0
\end{align}
introduces no further modification, when turning from the Green function to the S-matrix-element. The residues of the propagator are $Z = 1$ in on-shell renormalization. Furthermore the on-shell condition for the mass renormalization
\begin{align}
\left.\Sigma(p^2)\right|_{p^2 = m^2} = 0
\end{align}
means that the physical mass equals the tree level mass.

\subsection{The Squark Production Cross Section at Next-to-Leading Order}
The squark production cross section at next-to-leading order is composed out of three contributions. These are the Born (tree-level) cross section, the virtual and the real corrections. 
\begin{align}
\sigma^{\mathrm{NLO}} = \sigma^{\mathrm{B}} + \sigma^{\mathrm{V}} + \sigma^{\mathrm{R}}\label{eq:BVR}
\end{align}
All three contributions have to be calculated with next-to-leading order parton density functions and $\alpha_s$. There are seven mass scales: the squark mass $m_{\tilde{q}}$, the gluino mass $m_{\tilde{g}}$, the center of mass energy of the colliding protons which is set to $\sqrt{S} = \unit[13]{TeV}$, the top-quark mass which is fixed to $m_t = \unit[172]{GeV}$, the mass of the pseudoscalar $m_{\sigma}$ and the renormalization and factorization scale. They have been set to $\mu_F = \mu_R = m_{\tilde{q}}$. The next section summarizes how the calculation has been automated within a \texttt{C++} program.

@@

	\node [block1a] at (-1,-2.1) (notebookR) {soft/collinear limit: \newline \texttt{FeynArts} $\to \mathcal{M}^{\mathrm{R}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{R}|^2}$};
	\node [block1a] at (-1,-8) (notebookB) {\texttt{FeynArts} $\to \mathcal{M}^{\mathrm{B}}$ \newline \texttt{FormCalc} $\to$ $\sum |\mathcal{M}^{\mathrm{B}|^2}$};	

@@

	\node [block5b] at (7.5,-7.35) (Virt) {\underline{Virtual corrections}\newline \texttt{LoopTools} $\to$ \newline computation of $ 2 \sum \Re(\mathcal{M}^{\mathrm{B}}\mathcal{M}^{\mathrm{1L}\ast})$ \newline \texttt{CUBA} $\to$ \newline integration over \newline $t, x_1, x_2$ to $\sigma^{\mathrm{V}}$ };
	\node [block5c] at (11.5,-5.1) (Real) {\underline{Real corrections}\newline phase space slicing: \newline $\bullet$ soft/collinear part \newline from \texttt{Mathematica},\newline \texttt{CUBA} three dimen- \newline sional integration to $\sigma^{\mathrm{R}}_{\mathrm{S}}$ and $\sigma^{\mathrm{R}}_{\mathrm{HC}}$ \newline $\bullet$ hard non-collinear \newline part from \newline \texttt{MADGRAPH}, \newline  \texttt{CUBA} $\to$ seven \newline dimensional \newline integration to $\sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$ \newline $\sigma^{\mathrm{R}} = \sigma^{\mathrm{R}}_{\mathrm{S}} + \sigma^{\mathrm{R}}_{\mathrm{HC}} + \sigma^{\mathrm{R}}_{\mathrm{H} \overline{\mathrm{C}}}$};

@@

\caption{This scheme illustrates the setup of the computation of the next-to-leading order cross section. The (absolute) squared matrix amplitudes of the Born contribution the virtual corrections and the real corrections in the soft and/or collinear limit are generated by \texttt{Mathematica} packages and imported into a \texttt{C++} code. The amplitude from the real corrections is in the soft and collinear limit analytically integrated over the gluon's four-momentum in $D$ dimensions. Loop integrals are evaluated numerically using \texttt{Looptools}. For the hard non-collinear regime, the matrix amplitude of the real corrections is imported from \texttt{MadGraph5}. The \texttt{CUBA}-library was used for all three contributions to perform the remaining integration to arrive at the cross sections $\sigma^{\mathrm{B}}$, $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$.}\label{fig:CalcSetup}

@@

The computation of the real corrections has been done by Wojciech Kotlarski, another member of the group. To extract the singularities from the real corrections, the ``two cut phase space slicing method'', outlined in section \ref{sec:RealGluonRad}, has been used. For the soft and hard collinear limit, the absolute squared matrix element has been calculated with \texttt{FormCalc} and analytically integrated over the gluon's four-momentum in $D$ dimensions in \texttt{Mathematica}. This has been exported to the \texttt{C++} code to perform the rest of the integration numerically with the \texttt{CUBA} library. The matrix element in the hard non-collinear regime has been imported from \texttt{MadGraph5}\cite{Alwall:2014hca} and the whole integration has been performed numerically by the \texttt{CUBA} library.\\

@@

It has been checked for multiple different and quite distinct choices of the parameters $m_{\tilde{q}}$ and $m_{\tilde{g}}$ that the double as well as the single poles of the virtual and real corrections cancel up to machine precision. Regarding the virtual corrections, this has been done by numerically extracting the $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$ coefficient of loop integrals (see the discussion in section \ref{sec:SetLambdaExplanation} for more details).\\

@@

For the discussion of results it will not be distinguished between virtual and real corrections. This is because they have not been separated strictly in the calculation: As already discussed, both $\sigma^{\mathrm{V}}$ and $\sigma^{\mathrm{R}}$ are divergent, i.e. there are poles of the form $\frac{1}{\epsilon}$ and $\frac{1}{\epsilon^2}$. But these pole cancel exactly. On the other hand there are also prefactors from the phase space integral and the loop integral, which can be expanded in a power series in $\epsilon$. In short, the virtual and real correction to the cross section can be expressed with some coefficients $A$ - $E$, which are functions of the parameters $m_{\tilde{g}}$, $m_{\tilde{q}}$ and $m_{\sigma}$, in the following way:

@@

Some of the prefactors, namely $P_1$ and $P_2$, are the same in both contributions. Keeping them in eq. \eqref{eq:prefactoredecomp} would slow the computation of the real part down by a factor of about five because this part of the calculation is done analytically. Therefore a speed-up can be achieved by discarding the common prefactors at the cost of loosing track about the origin of the next-to-leading order corrections.\\
One common prefactor comes from the two-body phase space integral in eq. \eqref{eq:diffsigma}:

@@

In addition, the prefactor of a loop integral defined in \texttt{LoopTools} differs from the one usually (and therefore also here) used. The \texttt{LoopTools} definition\cite{LoopToolsManual} of a loop integral is 

@@

where $T^1$ is an $A$-integral, $T^2$ is a $B$-integral, etc. and $r_\Gamma = \frac{\Gamma(1-\epsilon)^2\Gamma(1+\epsilon)}{\Gamma(1-2\epsilon)}$, where $\Gamma(z)$ is the Gamma function. Comparing the prefactors of eq. \eqref{eq:LoopToolsInt} and eq.  \eqref{eq:LoopInt} one finds that one has to multiply the \texttt{LoopTools} output by

@@

in order to have the same prefactors as in eq. \eqref{eq:LoopInt}. Without going into detail why these factors are chosen, the right hand side of eq. \eqref{eq:PhasePrefactor} and eq. \eqref{eq:LoopPrefactor} are the prefactors discarded in the computation. Instead, the prefactor $\left( 1 + \frac{\pi^2}{6}\epsilon^2 \right)$ has been included in the virtual correction. Therefore $P_1$ and $P_2$ are chosen like

@@

P_1 &=  2\ln 4\pi - 2\gamma_E - \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s},\\
P_2 &=  -\ln 4\pi \cdot\ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s} + \frac{1}{2} \ln^2 \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}  + \gamma_E^2 - \frac{\pi^2}{3} + \ln^2 4\pi - 2\gamma_E\ln 4\pi + \gamma_E \ln \frac{tu - m_{\tilde{q}}^4}{\mu^2 s}.  \nonumber

@@

It can be seen that the  $K$-factor increases with increasing squark mass and decreases with increasing gluino mass. Note that the sum of virtual and real corrections gets negative for very light squarks. But this region of parameter space is already excluded experimentally.

@@

Note further that within the real corrections, only gluon radiation is included. This is because quark radiation, as described in section \ref{sec:RealQuarkRad}, involves the treatment of on-shell singularities which have unfortunately not been dealt with, due to a limited time budget. However, \cite{Gavin:2013kga} suggests that quark radiation gives only a sub percent effect to the next-to-leading order cross section of squark production when $m_{\tilde{g}} < m_{\tilde{q}}$. Of course, this argument applies to the MSSM but as the only difference to the MRSSM comes from diagrams involving gluinos and sgluons, it provides also a strong argument for the suppression of quark radiation in the MRSSM. In fact, sgluons do not appear at all in diagrams contributing to real corrections. Furthermore, the change from Majorana to Dirac gluinos can never imply an amplification of processes involving gluinos. The reason for this is that if a gluino undergoes a chirality flip, due to its mass, the right handed part of it, namely the octino, does neither couple to quarks nor to squarks. However, the effect of quark radiation is thought to increase when $m_{\tilde{g}} > m_{\tilde{q}}$. This is quantified within the next section, when squark production in the MSSM is discussed. Nonetheless, quark radiation is by no means to be thought of a dominant contribution to squark production at next-to-leading order.\\

@@

\caption{$K$-factors of the process $pp \to \tilde{u}_L\tilde{u}_R$  in the MRSSM for a selected set of masses. The pseudoscalar mass is fixed to \mbox{$m_{\mathrm{\sigma}} = \unit[5000]{GeV}$}. For the calulation of $\sigma^{\mathrm{LO}}$ \texttt{MMHT2014LO} (LHAPDF ID: $25000$) are used as parton density functions, whereas for $\sigma^{\mathrm{NLO}}$ \texttt{MMHT2014NLO} (LHAPDF ID: $25100$) are used.}\label{tab:MRSSMKfactors}

@@

It can be seen that the $K$-factors depend strongly on the ratio $\frac{m_{\tilde{q}}}{m_{\tilde{g}}}$ but not that strongly on the masses themselves. This is also depicted in fig. \ref{fig:Kfactor_MRSSM} which shows the $K$-factors in the $m_{\tilde{q}}$-$m_{\tilde{g}}$ plane. The contour lines follow approximately rays from the origin. By performing the calculation without the shuffling of prefactors as explained in section \ref{sec:prefactors}, the raising of the $K$-factors for increasing values of $\frac{m_{\tilde{q}}}{m_{\tilde{g}}}$ has been traced down to the real corrections. As quark radiation is not included, this effect can further be pinned down to originate from the diagrams in fig. \ref{fig:RealGluon}. However, at least for small $m_{\tilde{g}}$, fig. \ref{fig:Kfactor_MRSSM} suggests that the $K$-factors drop again for increasing $m_{\tilde{q}}$.

### 2016-07-13 RSymmetry.tex
Becky's remarks

In the MSSM the gauginos are Majorana particles. Their mass terms  reads in 2-spinor notation

@@

where $\chi$ is another Weyl-spinor. This means that the four-spinor of every gaugino is a Dirac- instead of a Majorana-spinor, e.g. for the gluino:

@@

In order to get a $R$-symmetric mass term on has to choose the $R$-charge of the new Weyl-spinor $\chi$ to be the opposite of $\lambda$.\\

@@

Observe that there is no 3 sgluon vertex, because of the antisymmetry of the structure constants $f^{abc}$. As already alluded to there are two distinct sgluons with different masses. The mass of the pseudoscalar $\sigma_0^a$ is given by the soft breaking parameter $m_{\sigma_0} = m_\sigma$ whereas the mass of the scalar $\phi_0$ is given by 

>>>>

In the MSSM the gauginos are Majorana particles. Their mass terms  reads in two-spinor notation

@@

where $\chi$ is another Weyl spinor. This means that the four-spinor of every gaugino is a Dirac  instead of a Majorana spinor, e.g. for the gluino:

@@

In order to get a $R$-symmetric mass term on has to choose the $R$-charge of the new Weyl spinor $\chi$ to be the opposite of $\lambda$.\\

@@

Observe that there is no three sgluon vertex, because of the antisymmetry of the structure constants $f^{abc}$. As already alluded to there are two distinct sgluons with different masses. The mass of the pseudoscalar $\sigma_0^a$ is given by the soft breaking parameter $m_{\sigma_0} = m_\sigma$ whereas the mass of the scalar $\phi_0$ is given by 
